Oregon_Wildfire_full

### 2017-03-03 r_scripts/oregon_clean.rmd
modified markdown file. fread function was stopping due to missing | seperator. Added fill = T. Also added overall time to run program

read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # about 20 mins

@@

### Output html?

>>>>

read_path <- paste0("../data/gan_episodes_of_care.txt")

# import the full dataframe, change column class to character
read_path <- paste0("../data/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T,fill = T, 
                   colClasses = rep("character", 72)) 
stop_time <-  Sys.time() - start_time

# Note RG: fill = T allows fread to fill in any missing data

# import time
stop_time # about 20 mins

@@

## Total Time Markdown File Ran
```{r}
stop_time2 <-  Sys.time() - start_time 
stop_time2
```
